---
title: "Assignment"
author: "Oriol Alcántara"
date: "10/4/2020"
output: html_document
---

# Package Description

'Assignment' pachage make an analysis, ploting and reading Fatality Analysis Reporting System (FARS) data
from the National Highway Traffic Safety
[link](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars).

[FARS](https://en.wikipedia.org/wiki/Fatality_Analysis_Reporting_System) is a nationwide census,
providing the American public yearly data, regarding faatal injuries suffered in motor vehicle traffic crashes.

# Load Packages

```{r}
library(Assignment)
library(maps)
```

# Included Data

Data files located in:

```{r}
list.files(system.file('extdata'), package = 'Assignment')
```

## Package Functions

### Function 'make_filename'

This function returns file name and path to the data files:

```{r}
make_filename(2015)
```

### Function 'fars_read_years'

Function to add info to the next 'fars_summarize_years'

```{r}
fars_read_years(2013)
```

### Function 'fars_summarize_years'

This function summarizes yearly accidents data, by month and year

```{r}
plot(fars_summarize_years(2015))
fars_summarize_years(c(2015, 2014))
```

### Function 'fars_map_state'

Displays a map indicating the accidents locations

```{r}
fars_map_state(49, 2014)

